### 2023-12-25 sections/4-results.tex
plot tweaks

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/fashion-mnist-60000-lfd.png}\\
    \subcaption{Fashion-mnist}
    \label{fig:results:fashion-mnist-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/glove-25-1183514-lfd.png}\\
    \subcaption{Glove-25}
    \label{fig:results:glove-25-lfd}
    \end{subfigure}
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/sift-1000000-lfd.png}\\
    \subcaption{Sift}
    \label{fig:results:sift-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/random-1000000-lfd.png}\\
    \subcaption{A random dataset}
    \label{fig:results:random-lfd}
    \end{subfigure}
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/silva-2224640-lfd.png}\\
    \subcaption{Silva 18S metagenomics}
    \label{fig:results:silva-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/radio-ml-97920-lfd.png}\\
    \subcaption{RadioML}
    \label{fig:results:radioml-lfd}
    \end{subfigure}%

    \caption{Local fractal dimension vs. cluster depth across six datasets, grouped by decile of LFD and weighted by the cardinalities of the clusters.}
    \label{fig:results:lfd-plots}
\end{figure}
%% end LFD plots

>>>>

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/fashion-mnist-60000-lfd.png}\\
    % \subcaption{Fashion-mnist}
    \label{fig:results:fashion-mnist-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/glove-25-1183514-lfd.png}\\
    % \subcaption{Glove-25}
    \label{fig:results:glove-25-lfd}
    \end{subfigure}
    % \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/sift-1000000-lfd.png}\\
    % \subcaption{Sift}
    \label{fig:results:sift-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/radio-ml-97920-lfd.png}\\
    % \subcaption{RadioML}
    \label{fig:results:radioml-lfd}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/silva-2224640-lfd.png}\\
    % \subcaption{Silva 18S metagenomics}
    \label{fig:results:silva-lfd}
    \end{subfigure}%  
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/random-1000000-lfd.png}\\
    % \subcaption{A random dataset}
    \label{fig:results:random-lfd}
    \end{subfigure}
    % \vspace{1em}

    \caption{Local fractal dimension vs. cluster depth across six datasets, grouped by decile of local fractal dimension and weighted by the cardinalities of the clusters. The last dataset is randomly generated. The number in the header of each plot indicates the cardinality of the dataset.}
    \label{fig:results:lfd-plots}
\end{figure}
%% end LFD plots
